---
title: "Tree_learning"
author: "Neha"
date: "09/02/2020"
output: pdf_document
---
```{r}
require(ISLR)
require(tree)
attach(Carseats)
summary(Carseats)
# A histogram of the sales data column
hist(Sales)
# Make this binary based on distribution
High=ifelse(Sales<=8,"No","Yes")
#Rewrite into dataframe
Carseats=data.frame(Carseats, High)
```
```{r}
#fit a tree to the data
#Exclude Sales --- from the right-hand side of the formula, because the response is derived from it.
tree.carseats=tree(Sales~.-High,data=Carseats)
#summarize the tree data
summary(tree.carseats)
plot(tree.carseats)
#add text to tree splits
text(tree.carseats,pretty=0)
```
For a detailed summary of the tree, print it:
```{r}
tree.carseats
```
create a training and test set (250,150) split of the 400 observations, grow the tree on the training set, and evaluate its performance on the test set.
```{r}
set.seed(1001)
#Take 250 training samples
train=sample(1:nrow(Carseats),250)
#train a tree model
tree.carseats=tree(High~.-Sales,Carseats,subset=train)
#Plot the tree
plot(tree.carseats);text(tree.carseats,pretty=0)
#Predict on remaining data
tree.pred=predict(tree.carseats,Carseats[-train,],type="class")
with(Carseats[-train,],table(tree.pred,High))
#final accuracy
(72+33)/150
```

PRUNING TREE
This tree was grown to full depth, and might be too variable. We now use CV to prune it.
```{r}
#using the cross validation method
cv.carseats=cv.tree(tree.carseats,FUN=prune.misclass)
cv.carseats
plot(cv.carseats)
#Missclassification errors
prune.carseats=prune.misclass(tree.carseats,best=13)
plot(prune.carseats)
text(prune.carseats,pretty=0)
```

Missclassification is jumpy because there are many cross validation points.
To prune optimally, pick a middle value from graph, low error. (Like 13)
So the printed tree now has size 13 and is much easier to read.

We can now test how the pruned tree does on the test data.

```{r}
tree.pred=predict(prune.carseats,Carseats[-train,],type="class")
with(Carseats[-train,],table(tree.pred,High))
(72+32)/150
```
It has done about the same as our original tree. So pruning did not hurt us wrt misclassification errors, and gave us a simpler tree.