---
title: "Polynomial Functions: Non Linear Functions"
output: pdf_document
---
```{r}
require(ISLR)
attach(Wage)
```

Polynomial Regression

1: Single predictor with 4th degree polynomial

```{r}
summary(Wage)
```

```{r}
#4th degree polynomial for age input
fit = lm(wage~poly(age,4),data=Wage)
summary(fit)
```
Generating a plot of the function

```{r fig.height=6, fig.width=7}
#limits of age parameter
agelims = range(age)
#grid of age parameter max to min
age.grid = seq(from=agelims[1],to=agelims[2])
age.grid
```

Predicting with standard errors
```{r}
preds = predict(fit,newdata =list(age=age.grid),se=TRUE)
se.bands=cbind(preds$fit+2*preds$se,preds$fit-2*preds$se)
plot(age,wage,col="darkgrey")
lines(age.grid,preds$fit,lwd=2,col="blue")
matlines(age.grid,se.bands,col="blue",lty=2)
```
Here we get the two range polynomial bands. Along with fitted polynomial line.


Fitting Polynomials without R
```{r}
# I = identity function used for raising parameters to a power
fita=lm(wage~age+I(age^2)+I(age^3)+I(age^4),data=Wage)
summary(fita)
```
```{r}
plot(fitted(fit),fitted(fita))
```
```{r}
# We can see all the polynomial components differently
summary(fit)
```
If it's not a single predictor or regression then use annova.

Nested sequence of models:
```{r}
# just wage and education
fita=lm(wage~education,data=Wage)
# Wage education and age
fitb=lm(wage~education+age,data=Wage)
# age with degree two
fitc=lm(wage~education+poly(age,2),data=Wage)
fitd=lm(wage~education+poly(age,3),data=Wage)
#using annova with a sequence
anova(fita,fitb,fitc,fitd)

```
Model 3 and 4 are not needed. 

Fitting other than RSS models to polynomial functions; such as linear regression.
Using polynomial model to fit binary response variable, wage 250K+ = 1 or 0


```{r}
# Age condition

fit=glm(I(wage>250) ~ poly(age,3), data=Wage, family=binomial)
summary(fit)
```
```{r}
preds=predict(fit,list(age=age.grid),se=T)
se.bands=preds$fit + cbind(fit=0,lower=-2*preds$se,upper=2*preds$se)
se.bands[1:5,]
```
Predict fits model on a logit scale so to transform to a probability scale we need to apply the inverse logit
mapping 
$$p=\frac{e^\eta}{1+e^\eta}.$$
```{r}
prob.bands=exp(se.bands)/(1+exp(se.bands))
matplot(age.grid,prob.bands,col="blue",lwd=c(2,1,1),lty=c(1,2,2),type="l",ylim=c(0,.1))
#find how much data actually occured
points(jitter(age),I(wage>250)/10,pch="|",cex=.5)
```

We get a standard error band where the probabilities all lie between zero and one. We can see zeros (below 250K wage below and above 250K on top). Only around 4% gets more than 250K.